\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements} 


The research presented in this dissertation could not have been accomplished 
without the support and encouragement of colleagues, family, and friends.
I would particularly like to thank Aurelio for giving me the opportunity to work on 
this topic, for patiently guiding me through the challenges of a physics analysis, 
and most of all, for transmitting his optimistic and passionate scientific approach.
Special thanks go also to:
\begin{itemize}
\item Mario, Martine and Matteo for expertly leading IFAE and the ATLAS group, 
  and always being available to answer questions.
\item Diego, who introduced me to the joys and burdens of collider physics 
  and continued supporting me with wise words of advice.
\item Davide, who made me a better programmer, 
  and with whom I shared an important year of work, 
  setting the foundations of the work described in this dissertation.
\item Antonella, for all the useful advice about the thesis writing process.
\item Juan Antonio and Ezequiel, for the fruitful collaboration.
\item Allison, Clement and Dan, who joined the analysis 
  effort with enthusiasm and hard work.
\item Javier and Eve, for being so patient and helpful 
  while working together on the analysis framework.
\item my office mates during the past several month at IFAE, Garo and Roger,
  for helping me through linguistic and scientific issues.
\item Oscar and Angelo \& Viviana, for ensuring
  I had a social life outside of CERN.
\end{itemize} 

Most importantly, I would like to thank my family, in particular my
parents and grandparents, 
for the constant support they provided throughout the course of my studies.
In addition, I want to acknowledge Viviana and Alessandro for designing the
cover of this thesis.
Finally, I would like to mention a special person, Lyuda, 
who virtually stood by my side for all these years.
